%! Author = Sujal Singh
%! Date = 3/15/23

% Preamble
\documentclass[11pt]{article}

\title{\textbf{GSoC Proposal to Mitmproxy}}
\author{
    \href{https://github.com/sujaldev}{\color{black}Sujal Singh} \\ \href{mailto:gsoc@sujal.dev}
    {\color{black}\texttt{gsoc@sujal.dev}}
}
\date{\hrule}

\pagenumbering{gobble}


% Packages
\usepackage{amsmath}
\usepackage[letterpaper, total={7.5in, 10in}]{geometry}
\usepackage{titlesec}
\usepackage[
    pdfusetitle,
    pdfsubject={GSoC Proposal},
    pdfauthor={Sujal Singh},
    colorlinks=true,
    urlcolor=blue,
]{hyperref}

%% Fonts
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{color}
\usepackage{biblatex}


% Section Title Format
\titleformat{\section}[hang]{\Large\bfseries}{\thesection.\hspace{0.5em}}{0pt}{}

% Document
\begin{document}
    \maketitle


    % ------------------------------------------------------------------------------------------------------------------- %


    \section*{Background}
    \label{sec:background}
    \addcontentsline{toc}{section}{Background}
    \def\arraystretch{1.6}

    \begin{tabular}{|l|l|}
        \hline
        \textbf{Name}     & {Sujal Singh}                                               \\
        \hline
        \textbf{Slack}    & {sujaldev}                                                  \\
        \hline
        \textbf{Email}    & {\href{mailto:gsoc@sujal.dev}{\color{black}gsoc@sujal.dev}} \\
        \hline
        \textbf{Language} & {English}                                                   \\
        \hline
    \end{tabular}


    \section{Preferred coding languages and experience}
    \label{sec:preferred-languages}

    My preferred language is python as I've built many projects with it.\ I am also familiar with HTML/CSS/JS.\


    % ------------------------------------------------------------------------------------------------------------------- %


    \section{Previous usage with mitmproxy, Charles, Fiddler, ZAP, Burp, other Honeynet Project tools, honeypots and
    HTTP tools in general}
    \label{sec:previous-usage}

    \begin{itemize}
        \item I have used burp suite before to test a variety of websites.
        \item I reverse engineered a website which wouldn't let me open the developer tools with mitmproxy, and
        converted it into an \href{https://github.com/PlanetVormir/Redskull/}{api}.
        \item {
            I used mitmproxy to fix an
            \href{https://github.com/react-native-video/react-native-video/issues/2899#issuecomment-1291682463}{issue}
            I faced in a \href{https://github.com/PlanetVormir/BartonTV}{project} related to the
            previous point.
        }
    \end{itemize}


    % ------------------------------------------------------------------------------------------------------------------- %


    \section{Previous open source development experience}
    \label{sec:previous-experience}

    The largest project I've built so far is a
    \href{https://github.com/sujaldev/skylon}{browser rendering engine} from scratch.\ I've built many other projects,
    mostly alone, but I've also worked collaboratively on a
    \href{https://github.com/aayush-tripathi/JEEPYQREPLYBOT}{project} with an online friend.\ Other than that, I also
    try to fix issues in projects that I use.


    % ------------------------------------------------------------------------------------------------------------------- %


    \section{Current school and specialty/major at the school}
    \label{sec:educational-background}

    Currently I am not enrolled at any institution, I recently graduated from high school (June 2022) where I opted
    to study Physics, Chemistry, Mathematics, English and Computer Science.\ After that, I took a gap year to prepare
    for college entrance examinations, which were held in January 2023, with another attempt in April.


    % ------------------------------------------------------------------------------------------------------------------- %


    \section{Number of years attended there}
    \label{sec:how-many-years-have-you-attended-there?}

    I attended this school for 12 years.


    % ------------------------------------------------------------------------------------------------------------------- %


    \section{City/country of residence this summer}
    \label{sec:residence}

    New Delhi, India.


    % ------------------------------------------------------------------------------------------------------------------- %


    \section{Expected time available for this project}
    \label{sec:availability}

    I'm expecting to have about 5--9 hours a day.


    % ------------------------------------------------------------------------------------------------------------------- %


    \section{Jobs, summer classes, vacations, exams, and/or other commitments}
    \label{sec:commitments}

    I might have to go to colleges for the admission procedure on a few days and also college could begin session in
    August, besides that I don't foresee any commitments.


    % ------------------------------------------------------------------------------------------------------------------- %


    \section{Participation in any previous Summer of Code project}
    \label{sec:previous-participation}

    This is my first time applying to any Summer of Code project.


    % ------------------------------------------------------------------------------------------------------------------- %


    \section{Applications for any other GSoC project}
    \label{sec:other-applications}

    I have neither applied nor do I intend to apply for any other GSoC projects.


    % ------------------------------------------------------------------------------------------------------------------- %


    \section{URL for resume/CV}
    \label{sec:resume}

    \href{https://resume.sujal.dev}{resume.sujal.dev}


    % ------------------------------------------------------------------------------------------------------------------- %


    \section{Personal/blog URLs}
    \label{sec:personal-urls}

    My sibling and I recently acquired a home server and a public static IPv4 address, the domain
    \href{https://sujal.dev}{sujal.dev} points to it.\ While it currently does not host any public services, we plan
    on hosting host a lot of things (including a blog) post my exams.\ I am also hosting a lot of services on oracle's
    free servers on a separate domain.


    % ------------------------------------------------------------------------------------------------------------------- %


    \section{Project Plan}
    \label{sec:project-plan}

    \input{project-plan}


    % ------------------------------------------------------------------------------------------------------------------- %

\end{document}